Output Summary

### 2023-05-04 03-post-process/output-plots-children/03-fit-to-data.Rmd
Add colorized text describing meaning of line plots

In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).

@@

  if (j == 1) mtext(side = 2, "Pre-Spawn Survival", line = 1, cex = 0.9)
  # om = par("mar"); nm = om; nm[1] = 2; par(mar = nm); on.exit(par(mar = om))
  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = make_lim(0, jags_data$x_carcass_total),
               col = tran_cols["data"], border = main_cols["data"])
  at_x = axisTicks(par("usr")[1:2], log = FALSE)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$x_carcass_total[observable,j]), 3, 4)[at_x])
  box()

>>>>

Figures in this section show the consistencies between the `r colorize("posterior", main_cols["model"])` (mean with 95% equal-tailed credible interval) and the `r colorize("data", main_cols["data"])` (point estimate with approximate 95% confidence interval illustrating the magnitude of assumed observation error).

@@

  if (j == 1) mtext(side = 2, "Pre-Spawn Survival", line = 1, cex = 0.9)
  # om = par("mar"); nm = om; nm[1] = 2; par(mar = nm); on.exit(par(mar = om))
  mp = barplot(jags_data$x_carcass_total[observable,j], xaxt = "n", ylim = make_lim(0, jags_data$x_carcass_total),
               col = tran_cols["data"], border = main_cols["data"])
  at_x = axisTicks(par("usr")[1:2], log = FALSE)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$x_carcass_total[observable,j]), 3, 4)[at_x])
  box(col = par("col.axis"))

### 2023-05-04 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
Add colorized text describing meaning of line plots

These figures show the realized time series of egg-to-parr survival that include all sources of variability in red: that explained by Beverton-Holt dynamics and that not explained by it.

@@

Just the realized time series shown.

@@

The blue shows the time series with variability explained only by Beverton-Holt dynamics.

@@

The blue shows the time series with variability explained by Beverton-Holt dynamics and the carry-over residual.

@@

This is the scale the Beverton-Holt recruitment function is estimated on.

@@

  # draw state pairs + uncertainty
  segments(E["2.5%",], phi_E_Pb["mean",], E["97.5%",], phi_E_Pb["mean",], col = main_cols["model"])
  segments(E["mean",], phi_E_Pb["2.5%",], E["mean",], phi_E_Pb["97.5%",], col = main_cols["model"])
  points(phi_E_Pb["mean",] ~ E["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
  text(phi_E_Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

@@

  # draw state pairs + uncertainty
  segments(E["2.5%",], Pb["mean",], E["97.5%",], Pb["mean",], col = main_cols["model"])
  segments(E["mean",], Pb["2.5%",], E["mean",], Pb["97.5%",], col = main_cols["model"])
  points(Pb["mean",] ~ E["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
  text(Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

@@

This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model. The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.

@@

  if (j == 1) {
    legend("bottomright", title = "Eggs/Spawner:",
           legend = c("1,000", "1,800", "3,600"),
           lty = c(1,2,3), bty = "n", cex = 0.75)
  }
}

>>>>

@@

The `r colorize("realized time series", main_cols["model"])`.

@@

The `r colorize("realized time series", main_cols["model"])` and the `r colorize("time series with variability explained only by Beverton-Holt dynamics", main_cols["model2"])`.

@@

The `r colorize("realized time series", main_cols["model"])` and the `r colorize("time series with variability explained by Beverton-Holt dynamics and the carry-over residual", main_cols["model2"])`.

@@

This is the scale the Beverton-Holt recruitment function is modeled on.

@@

  # draw state pairs + uncertainty
  segments(E["2.5%",], phi_E_Pb["mean",], E["97.5%",], phi_E_Pb["mean",], col = main_cols["model"])
  segments(E["mean",], phi_E_Pb["2.5%",], E["mean",], phi_E_Pb["97.5%",], col = main_cols["model"])
  points(phi_E_Pb["mean",] ~ E["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
  text(phi_E_Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")

  box(col = par("col.axis"))
}

@@

  # draw state pairs + uncertainty
  segments(E["2.5%",], Pb["mean",], E["97.5%",], Pb["mean",], col = main_cols["model"])
  segments(E["mean",], Pb["2.5%",], E["mean",], Pb["97.5%",], col = main_cols["model"])
  points(Pb["mean",] ~ E["mean",], pch = 16, col = tran_cols["model"], cex = 1.8)
  text(Pb["mean",] ~ E["mean",], labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")

  box(col = par("col.axis"))
}

@@

This figure shows that total spawner abundance is a reasonable index of total egg production, according to the assumptions of our model (eggs = spawners-age-4/5 * 50% * age-specific fecundity).
The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.

@@

  if (j == 1) {
    legend("bottomright", title = "Eggs/Spawner:",
           legend = c("1,000", "1,800", "3,600"),
           lty = c(1,2,3), bty = "n", cex = 0.75)
  }

  box(col = par("col.axis"))
}

### 2023-05-04 03-post-process/output-plots-children/06-length-based-survival.Rmd
Add colorized text describing meaning of line plots

@@

##### Realized + Predicted

@@

#### Realized + Predicted

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       # ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
       ylim = phi_Mb_Ma_lim,
       xlim = range(L_Mb_seq), 
       main = pops[j]
  )

>>>>

The `r colorize("realized time series", main_cols["model"])`.

@@

##### Realized & Expected

The `r colorize("realized time series", main_cols["model"])` and `r colorize("expected time series", main_cols["model2"])` (i.e., without process noise).

@@

#### Realized & Expected

The `r colorize("realized time series", main_cols["model"])` and `r colorize("expected time series", main_cols["model2"])` (i.e., without process noise).

@@

  # make a blank plot with the correct dimensions
  plot(1,1, type = "n", 
       ylim = phi_Mb_Ma_lim,
       xlim = range(L_Mb_seq)
  )
  panel_label(pops[j])
